Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-06-18 awipev-CO2.Rmd
text updated

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******

@@

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
```

>>>>

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019

@@

p_ct_ts <- ggplot() +
    geom_point(data=discrete, aes(x= datetime, y= ct)) +
  labs(title= "",x="Time", y="CT (µmoles/kg)")+
    Mytheme()
p_at_ts <- ggplot() +
    geom_point(data=discrete, aes(x= datetime, y= at)) +
  labs(title= "",x="Time", y="AT (µmoles/kg)")+
    Mytheme()

@@

pdelta_at_snapo
pdelta_at_snapo_dygraph
p_at_ts
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
p_ct_ts
ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
```
```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
# d_hour is the real data set that is read at the beginning of the script
# d_all comprises additional columns calculated in this script
# These additional variablrs are useful elsewhere (for example in "presentation")
# Hence, here we save it for this use
save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
```
